SNP Analysis

### 2018-07-17 SNP_Prediction_Analysis.Rmd
...

```{r setup, include=FALSE}
library(ggplot2)
library(gridExtra)
library(glmnet)
library(pander)
library(readxl)
library(pROC)

@@

```{r, echo=F, warning=F, fig.height=10, fig.width=8}

@@

# Adjust based on the summary values per CN that we get in WGS (mostly) NP Barrett's cases
adjust.segraw<-function(segraw) {
  segraw = segraw %>% rowwise() %>% dplyr::mutate( total = nMajor+nMinor )
  segraw = subset(segraw, chr %in% c(1:22))

  segraw$adjLRR = NA
  for (cn in unique(segraw$total)) {
    rows = which(segraw$total == cn)
    values = seg[rows, 'medLRR', drop=T]

@@

    #}
    #segraw[rows,][['adjLRR']] = newM + (values - mean(values)) * (newSD/sd(values))

    segraw[rows,'adjLRR'] = values * predict(fitM, newdata=cbind.data.frame('y'=values)) - cn)
  }  
segraw  
}

@@

m = (melt(seg, measure.vars=c('medLRR','adjLRR')))
ggplot(m, aes(total, value, group=total)) + facet_grid(~variable) + geom_boxplot() + labs(title=pt)

@@

```{r rnormals, echo=F, warning=F, message=F, fig.width=10, fig.height=8}
randNormal = sample(rownames(normalSegs), 1)
pt = unlist(strsplit(randNormal, '_'))[1]
segs = subset(segments.list[[pt]], chr %in% c(1:22) & grepl(sub('_', '.*', randNormal),sample))
segs$chr = factor(segs$chr, levels=c(1:22), ordered = T)

@@

qqnorm(allDf, main='Normal Q-Q plot, sWGS')
qqnorm(arrayDf, main='Normal Q-Q plot, SNP arrays')

@@

@@

pred.qc = cbind.data.frame(preds, qc)
dim(pred.qc)
table(pred.qc$Status)

@@

# pred.qc.ex = subset(pred.qc, !exclude)
# cuts = seq(0,1,0.1)
# 
# pred.qc.ex$quants = with(pred.qc.ex, cut(Prob, breaks=cuts))
# qt = as.data.frame.matrix(table(pred.qc.ex$quants, pred.qc.ex$Status))
# qt$quant = rownames(qt)

>>>>

```{r setup, include=FALSE}
library(ggplot2)
library(gridExtra)
library(glmnet)
library(pander)
library(readxl)
library(pROC)
library(ggfortify)

@@

```{r, echo=F, warning=F, fig.height=10, fig.width=8,eval=F}

@@

fitCN = lm(y~x, data=b)

# Adjust based on the summary values per CN that we get in WGS (mostly) NP Barrett's cases
adjust.segraw<-function(segraw) {
  segraw = segraw %>% rowwise() %>% dplyr::mutate( total = nAraw+nBraw )
  segraw = subset(segraw, chr %in% c(1:22))

  segraw$adjLRR = NA
  #for (cn in unique(segraw$total)) {
  #  rows = which(segraw$total == cn)
  #  values = seg[rows, 'medLRR', drop=T]

@@

    #}
    #segraw[rows,][['adjLRR']] = newM + (values - mean(values)) * (newSD/sd(values))
   # smy
    #median(predict(fitM, newdata=cbind.data.frame('y'=values)))-cn

    new = predict(fitCN, newdata=cbind.data.frame('x'=segraw$total))
    #plot(scale(new, center = T))

    segraw[,'adjLRR'] = scale(new,center=T)

   # segraw[rows,'adjLRR'] = (values * (predict(fitM, newdata=cbind.data.frame('y'=values)) - cn))
  #}  
segraw  
}

@@

m = (melt(seg, measure.vars=c('medLRR','adjLRR')))
m$total = round(round(m$total, 1))
ggplot(m, aes(total, value, group=total)) + facet_grid(~variable) + geom_boxplot() + labs(title=pt)

@@

```{r rnormals, echo=F, warning=F, message=F, fig.width=10, fig.height=8, eval=F}
randNormal = sample(rownames(normalSegs), 1)
pt = unlist(strsplit(randNormal, '_'))[1]
segs = subset(segments.list[[pt]], chr %in% c(1:22) & grepl(sub('_', '.*', randNormal),sample))
segs$chr = factor(segs$chr, levels=c(1:22), ordered = T)

@@

grid.arrange(
  ggplot( melt(allDf), aes(sample=value)) + stat_qq() + labs(title='Normal Q-Q plot, sWGS'),
  ggplot( melt(arrayDf), aes(sample=value)) + stat_qq() + labs(title='Normal Q-Q plot, SNP arrays'),
  ncol=1
)

@@

length(which(preds.normal$Prob > 0.5))/nrow(preds.normal)

@@

pred.qc = cbind.data.frame(preds, qc)
#dim(pred.qc)
#table(pred.qc$Status)

@@

pred.qc.ex = subset(pred.qc, !exclude)
cuts = seq(0,1,0.1)

pred.qc.ex$quants = with(pred.qc.ex, cut(Prob, breaks=cuts))
qt = as.data.frame.matrix(table(pred.qc.ex$quants, pred.qc.ex$Status))
qt$quant = rownames(qt)
pander(qt)
